Depression_Vis

### 2023-04-12 Depression_Vis.Rmd
date plots

#Create the Depression Line Graph by Year
ggplot(data=subset(Mothership_Mean_CUDOS_Year,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUDOS,group=TxYear,color=TxYear))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Depression Severity by Treatment Year During Partial Hospitalization")+
    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Depression Severity",limits=c(20,36,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559","#4B5D8E"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

Break it up by duration group (Year)
```{r, include= FALSE}
#Create a New Data Set with an Average Depression Variable and Gender
YEARTXDF1<-Mothership_Long %>%
  filter(Duration == "1-5") %>%
  group_by(TxDay,TxYear) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
YEARTXDF1<-YEARTXDF1[1:50,]
# plot
YEARTX1<-ggplot(data=subset(YEARTXDF1,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUDOS,group=TxYear,color=TxYear))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    title ="Depression Severity by YEARTX During Partial Hospitalization",
    subtitle = "Patient discharge 1-5 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

@@

YEARTXDF2<-YEARTXDF2[1:100,]

# plot
YEARTX2<-ggplot(data=subset(YEARTXDF2,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUDOS,group=TxYear,color=TxYear))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    title ="Depression Severity by YEARTX During Partial Hospitalization",
    subtitle = "Patient discharge 6-10 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

@@

YEARTXDF3<-YEARTXDF3[1:150,]

# plot
YEARTX3<-ggplot(data=subset(YEARTXDF3,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUDOS,group=TxYear,color=TxYear))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(title ="Depression Severity by YEARTX During Partial Hospitalization",
    subtitle = "Patient discharge 11-15 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

##### 16+ Days
YEARTXDF4<-Mothership_Long %>%
  filter(Duration == "16+") %>%
  group_by(TxDay,TxYear) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
YEARTXDF4<-YEARTXDF4[1:200,]

# plot
YEARTX4<-ggplot(data=subset(YEARTXDF4,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUDOS,group=TxYear,color=TxYear))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(title ="Depression Severity by YEARTX During Partial Hospitalization",
    subtitle = "Patient discharge 16+ days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

>>>>

#Create the Depression Line Graph by Year
ggplot(data=subset(Mothership_Mean_CUDOS_Year,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUDOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Depression Severity by Treatment Year During Partial Hospitalization")+
    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Depression Severity",limits=c(20,36,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559","#4B5D8E"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

Break it up by duration group (Year)
```{r, include= FALSE}
#Create a New Data Set with an Average Depression Variable and Gender
YEARTXDF1<-Mothership_Long %>%
  filter(Duration == "1-5") %>%
  group_by(TxDay,TxYear) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
YEARTXDF1<-YEARTXDF1[1:40,]
# plot
YEARTX1<-ggplot(data=subset(YEARTXDF1,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUDOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    title ="Depression Severity by YEARTX During Partial Hospitalization",
    subtitle = "Patient discharge 1-5 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

@@

YEARTXDF2<-YEARTXDF2[1:80,]

# plot
YEARTX2<-ggplot(data=subset(YEARTXDF2,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUDOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    title ="Depression Severity by YEARTX During Partial Hospitalization",
    subtitle = "Patient discharge 6-10 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

@@

YEARTXDF3<-YEARTXDF3[1:120,]

# plot
YEARTX3<-ggplot(data=subset(YEARTXDF3,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUDOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(title ="Depression Severity by YEARTX During Partial Hospitalization",
    subtitle = "Patient discharge 11-15 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

##### 16+ Days
YEARTXDF4<-Mothership_Long %>%
  filter(Duration == "16+") %>%
  group_by(TxDay,TxYear) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
YEARTXDF4<-YEARTXDF4[1:180,]

# plot
YEARTX4<-ggplot(data=subset(YEARTXDF4,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUDOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(title ="Depression Severity by YEARTX During Partial Hospitalization",
    subtitle = "Patient discharge 16+ days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```
